### 2011-01-26 Text/paper.tex
Added graphs for train simulations. Something is wrong with the steady state.

\section{Capillary number region}
The same as in the previous example can help us to identify the necessary capillary regime. The
most important thing is to establish different accentricity factors.
\section{Simulation setup}

>>>>

\section{Capillary number region}
The same as in the previous example can help us to identify the necessary capillary regime. The
most important thing is to establish different accentricity factors.

\section{Train simulation}
As far as the requirements for the grid are ``heavy'' we performed a bunch of simulations to
examine how the distance between bubbles influences on the thickness. For this purpose the
simulation was conducted on the grid 82x82x750. We examined different initialized distances between
bubbles. The initial lengths of bubbles were chosen as $300$, $350$, $400$, $450$, $500$, $550$
lattice units. Therefore, the corresponding initial distances between bubbles are
$450$,$400$,$350$,$300$,$250$ lattice units. On the steady state regime the distances become $386$,
$317$, $248$,$176$,$99$,$23$ lattice units. The corresponding capillary numbers calculated based on
the center bubble velocity are as follows $0.905$, $0.986$,$1.08$,$1.19$, $1.33$, $1.49$. The
calculated radiuses (diagonal radius equal to the axes radius) are as follows
$0.783$,$0.778$,$0.772$,$0.764$,$0.753$,$0.747$. Thus, one can see the great impact of the bubbles
on each other velocity for the given body force. However, in terms of the film thicknesses those
numbers look adequate. One can see the film thicknesses dependency on the capillary number for the
\citeauthor{heil-threedim} and bubble train simulations data in Fig. \ref{fig:capillaries:train}. 
\begin{figure}
\includegraphics[width=0.97\textwidth]{Figures/capillaries_comparison_train.eps}
\caption{Some more information on representing \label{fig:capillaries:train}}
\end{figure}

\section{Simulation setup}
